---
title: "REP Grant Proposal -- Power Analysis Technical Appendix"
subtitle: "Benchmark Effect Size: Cohen's d = 0.55"
author: "WCER School Mental Health Collaborative"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_notebook:
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: false
      smooth_scroll: true
    number_sections: true
    df_print: paged
    theme: flatly
    highlight: tango
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    df_print: paged
    theme: flatly
    highlight: tango
    code_folding: show
    fig_caption: true
  word_document:
    toc: true
    toc_depth: 3
    number_sections: true
    fig_caption: true
fontsize: 11pt
geometry: margin=1in
always_allow_html: true
editor_options:
  chunk_output_type: inline
---

## Overview

This notebook reproduces the power analysis for the **Resilience Education Program
(REP)** randomized controlled trial (RCT), submitted as a technical appendix to a
NIMH grant proposal. It uses **Cohen's d = 0.55** as the benchmark effect size,
derived from pilot REP findings.

The analysis provides:

- Analytic estimates of required sample sizes and minimum detectable effects (MDEs)
- Sensitivity analyses across ICC and R² assumptions
- Simulation-based power for moderation (Treatment × Moderator interaction) and
  mediation (indirect effect) models
- Reproducible environment management via **`renv`**

All computations use **R 4.4.1** with the **pwr**, **simr**, and **mediation**
packages. All outputs are saved to `figures/`, `tables/`, and `data/`.

> **Data availability:** All analyses use **simulated data** generated within R.
> No external participant data are required, ensuring full reproducibility from
> this file alone.

---

## 1. Setup

### 1.1 Reproducibility

```{r reproducibility, message=FALSE, warning=FALSE}
set.seed(12345)
R.version.string

if (!requireNamespace("renv", quietly = TRUE)) install.packages("renv")
if (file.exists("renv.lock")) {
  suppressMessages(renv::restore(prompt = FALSE))
} else {
  suppressMessages(renv::init(bare = TRUE))
  suppressMessages(renv::snapshot(prompt = FALSE))
}
cat("renv environment ready.\n")
```

### 1.2 Packages

```{r packages, message=FALSE, warning=FALSE}
pkgs <- c("pwr", "dplyr", "tibble", "tidyr", "purrr", "stringr",
          "ggplot2", "scales", "readr", "knitr", "lme4", "simr",
          "mediation", "officer", "flextable", "writexl", "gt", "webshot2")

invisible(lapply(pkgs, function(p) {
  if (!requireNamespace(p, quietly = TRUE)) install.packages(p, quiet = TRUE)
}))
invisible(lapply(pkgs, library, character.only = TRUE))

# Output directories (relative paths -- no hardcoded network drives)
dir.create("figures", showWarnings = FALSE)
dir.create("tables",  showWarnings = FALSE)
dir.create("data",    showWarnings = FALSE)

cat("Packages loaded. Output folders ready.\n")
```

---

## 2. Helper Functions

Five reusable functions underpin all analytic calculations. Table B0 summarizes
their purpose and arguments.

```{r helper-table}
helper_table <- tibble::tibble(
  Function      = c("design_effect()", "d_adjust()", "required_N()",
                    "power_at_N()",    "MDE_at_N()"),
  Description   = c(
    "Computes the design effect to adjust for clustering.",
    "Adjusts effect size for covariate-explained variance (R²).",
    "Computes total required N given effect size, power, and DE.",
    "Estimates achieved power for fixed N and DE.",
    "Computes minimum detectable effect for fixed N and target power."
  ),
  `Key Arguments` = c("icc, mbar", "d, R2", "d, R2, power, alpha, DE",
                      "N_total, d, R2, alpha, DE", "N_total, power, R2, alpha, DE"),
  Output        = c("Design effect multiplier", "Adjusted effect size (dz)",
                    "Total sample size (N_total)", "Estimated power (p)",
                    "Minimum detectable effect (MDE)")
)

knitr::kable(helper_table,
  caption = "*Table B0.* Summary of helper functions for the REP power analysis.",
  align   = c("l", "l", "l", "l"))
```

```{r helper-functions}
# Global significance level (two-tailed)
alpha <- 0.05

#' Design effect from ICC and average cluster size.
design_effect <- function(icc = 0.07, mbar = 9) 1 + (mbar - 1) * icc

#' Adjust Cohen's d for covariate-explained variance R².
d_adjust <- function(d, R2) d / sqrt(1 - R2)

#' Total sample size for target power, accounting for design effect.
required_N <- function(d, R2 = 0, power = 0.80, alpha = 0.05, DE = 1.00) {
  dz      <- d_adjust(d, R2)
  z_alpha <- qnorm(1 - alpha / 2)
  z_beta  <- qnorm(power)
  N_per_group_noDE <- 2 * (z_alpha + z_beta)^2 / dz^2
  ceiling(DE * N_per_group_noDE)
}

#' Statistical power at a fixed total N (approximate two-sample formula).
power_at_N <- function(N_total, d, R2 = 0, alpha = 0.05, DE = 1.00) {
  dz          <- d_adjust(d, R2)
  n_per_group <- (N_total / DE) / 2
  se_d        <- sqrt(2 / n_per_group)
  pnorm(abs(dz) / se_d - qnorm(1 - alpha / 2))
}

#' Minimum detectable effect (MDE) at a fixed total N.
#' N_total already incorporates the design effect; SE is scaled accordingly.
MDE_at_N <- function(N_total, power = 0.80, R2 = 0, alpha = 0.05, DE = 1.56) {
  n_per_group <- (N_total / DE) / 2
  se_d        <- sqrt(2 / n_per_group)
  dz_star     <- (qnorm(1 - alpha / 2) + qnorm(power)) * se_d
  dz_star * sqrt(1 - R2)
}
```

---

## 3. Required Sample Sizes -- Benchmark Effect

The benchmark effect size **d = 0.55** is derived from pilot REP data. Table B1
shows the total sample sizes required to achieve **80% power** across combinations
of covariate adjustment (R²) and clustering (DE).

The design effect **DE = 1.56** reflects an ICC of 0.07 with an average cluster
size of 9 students (typical for school-based interventions).

```{r required-n-table}
DE_grid <- c(`No clustering (DE = 1.00)` = 1.00,
             `Clustered (DE = 1.56)`     = design_effect(icc = 0.07, mbar = 9))
R2_grid <- c(0.00, 0.30, 0.50)

table_requiredN <- tidyr::expand_grid(R2 = R2_grid, DE_lab = names(DE_grid)) |>
  dplyr::mutate(
    DE         = unname(DE_grid[DE_lab]),
    Required_N = purrr::pmap_dbl(
      list(0.55, R2, 0.80, alpha, DE),
      ~ required_N(..1, R2 = ..2, power = ..3, alpha = ..4, DE = ..5)
    ),
    Effect = "d = 0.55",
    Power  = 0.80
  ) |>
  dplyr::select(Effect, Power, R2,
                `Design Effect` = DE_lab,
                `Required N`    = Required_N)

knitr::kable(
  table_requiredN,
  digits      = c(NA, 2, 2, NA, 0),
  caption     = "*Table B1.* Required total sample sizes (N) to detect d = 0.55 at 80% power under varying R² and clustering conditions.",
  col.names   = c("Effect", "Power (1–β)", "R²", "Design Effect (DE)", "Required N"),
  align       = c("l", "c", "c", "c", "c")
)
cat("\n*Note.* DE = design effect; R² = proportion of variance explained by covariates.\n")
```

---

## 4. Sensitivity Analysis -- Planned N = 163

The planned sample size of **N = 163** was selected to accommodate the design
effect from clustering. This section reports the achieved power and MDE for that
fixed N across R² levels.

```{r sensitivity-table}
planned_N  <- 163
DE_planned <- design_effect(icc = 0.07, mbar = 9)  # 1.56

sensitivity <- tibble::tibble(R2 = R2_grid) |>
  dplyr::mutate(
    `Power (1–β)`    = purrr::map_dbl(R2, ~ power_at_N(planned_N, 0.55,
                                                         R2 = ., DE = DE_planned)),
    `MDE (Cohen's d)` = purrr::map_dbl(R2, ~ MDE_at_N(planned_N, power = 0.80,
                                                        R2 = ., DE = DE_planned))
  )

knitr::kable(
  sensitivity,
  digits    = c(2, 2, 2),
  caption   = "*Table B2.* Estimated power and MDE for N = 163 (DE = 1.56) across R² levels.",
  col.names = c("R²", "Power (1–β)", "MDE (Cohen's d)"),
  align     = c("c", "c", "c")
)
cat("\n*Note.* MDE = minimum detectable effect; DE = design effect from clustering.\n")
```

### 4.1 MDE by Sample Size (Table B2 Word Export)

```{r mde-table-export}
mde_results <- expand.grid(R2 = R2_grid, Sample_Size = c(81, 162)) |>
  dplyr::arrange(Sample_Size, R2) |>
  dplyr::mutate(
    MDE = round(MDE_at_N(Sample_Size, power = 0.80, R2 = R2, DE = 1.56), 2)
  ) |>
  dplyr::select(Sample_Size, R2, MDE)

# Export to Word
word_path <- "tables/Table_B2_MDE.docx"
doc <- officer::read_docx() |>
  officer::body_add_par(
    "Table B2. Minimum Detectable Effect (MDE) by R² and Sample Size (DE = 1.56)",
    style = "heading 2"
  ) |>
  flextable::body_add_flextable(
    flextable::autofit(flextable::qflextable(mde_results))
  ) |>
  officer::body_add_par(
    "*Note.* MDE = Minimum Detectable Effect. DE = 1.56.",
    style = "Normal"
  )
print(doc, target = word_path)
cat("Saved:", word_path, "\n")
```

---

## 5. Simulation -- Moderation Power

This section estimates power to detect a **Treatment × Moderator interaction**
using a multilevel model via the `simr` package. Students are nested within
schools (random intercepts); ICC ≈ 0.07.

**Parameters:** Treatment effect (β = 0.40), interaction effect (β = 0.55),
baseline covariate (β = 0.50), N = 163 across 20 schools.

```{r moderation-sim, message=FALSE, warning=FALSE}
set.seed(1234)

# --- Design parameters ---
n_schools    <- 20
m_per_school <- round(planned_N / n_schools)
b_treat      <- 0.40
b_intx       <- 0.55
b_pre        <- 0.50
sigma_school <- 0.30
sigma_eps    <- 1.08
icc_empirical <- sigma_school^2 / (sigma_school^2 + sigma_eps^2)

# --- Simulate clustered dataset ---
school <- factor(rep(1:n_schools, each = m_per_school))
treat  <- rbinom(length(school), 1, 0.5)
mod    <- rbinom(length(school), 1, 0.5)
pre    <- rnorm(length(school))
u0     <- rnorm(n_schools, 0, sigma_school)
y      <- u0[as.integer(school)] +
          b_treat * treat + b_intx * (treat * mod) + b_pre * pre +
          rnorm(length(school), 0, sigma_eps)
dat    <- data.frame(y, treat = factor(treat), mod = factor(mod), pre, school)

# --- Fit multilevel model ---
m0 <- suppressWarnings(
  lme4::lmer(y ~ treat * mod + pre + (1 | school), data = dat,
             control = lme4::lmerControl(check.conv.singular = "ignore"))
)

# --- Monte Carlo power simulation ---
m0_sim <- simr::makeLmer(
  y ~ treat * mod + pre + (1 | school),
  lme4::fixef(m0), lme4::VarCorr(m0), data = dat
)

pow_mod <- suppressWarnings(
  simr::powerSim(m0_sim, test = simr::fixed("treat1:mod1", "t"),
                 nsim = 200, progress = FALSE)
)

# --- Extract power estimate ---
extract_val <- function(pattern, text, div = 1) {
  m <- regexec(pattern, text, perl = TRUE)
  r <- regmatches(text, m)
  if (length(r) && length(r[[1]]) >= 2) as.numeric(r[[1]][2]) / div else NA_real_
}
txt       <- paste(capture.output(print(pow_mod)), collapse = " ")
est_power <- extract_val("Power\\s*=\\s*([0-9.]+)\\s*%", txt, 100)
if (is.na(est_power)) est_power <- mean(pow_mod$pval < 0.05, na.rm = TRUE)

se_power <- sqrt(est_power * (1 - est_power) / 200)
ci_low   <- max(0, est_power - 1.96 * se_power)
ci_high  <- min(1, est_power + 1.96 * se_power)

# --- Table B3 ---
power_summary <- data.frame(
  `Fixed Effect`          = "Treatment × Moderator",
  `ICC`                   = round(icc_empirical, 2),
  `Simulations`           = 200,
  `Estimated Power (1–β)` = round(est_power, 2),
  `SE`                    = round(se_power, 3),
  `95% CI Lower`          = round(ci_low, 2),
  `95% CI Upper`          = round(ci_high, 2),
  check.names = FALSE
)

knitr::kable(
  power_summary,
  caption = "*Table B3.* Estimated power for the Treatment × Moderator interaction (N = 163; DE = 1.56; ICC ≈ 0.07; 200 simulations).",
  align   = c("l", "c", "c", "c", "c", "c", "c"),
  digits  = 2
)
cat("\n*Note.* Power estimated via Monte Carlo simulation (simr::powerSim).\n")
```

### 5.1 Power Curves -- Schools and Within-Cell

```{r power-curves, message=FALSE, warning=FALSE}
set.seed(1234)
simr::simrOptions(progress = FALSE)

int_term <- if ("treat1:mod1" %in% names(lme4::fixef(m0))) "treat1:mod1" else "treat:mod"

# Helper: coerce powerCurve to data.frame robustly
pc_to_df <- function(pc) {
  df <- tryCatch(as.data.frame(pc), error = \(e) NULL)
  if (!is.null(df)) return(df)
  df <- tryCatch(as.data.frame(summary(pc)), error = \(e) NULL)
  if (!is.null(df)) return(df)
  sn  <- methods::slotNames(pc)
  out <- lapply(c("x","y","lwr","upr","n"), \(nm) if (nm %in% sn) methods::slot(pc, nm))
  as.data.frame(Filter(Negate(is.null), setNames(out, c("x","y","lwr","upr","n")[
    vapply(c("x","y","lwr","upr","n"), \(nm) nm %in% sn, logical(1))])))
}

# Curve A: vary number of schools
breaks_sch     <- c(8, 10, 12, 14, 16, 18, 20, 24, 28, 32)
m_extended     <- simr::extend(m0, along = "school", n = max(breaks_sch))
pc_school      <- simr::powerCurve(m_extended, test = simr::fixed(int_term, "t"),
                                   along = "school", breaks = breaks_sch, nsim = 200)
pc_school_tbl  <- pc_to_df(pc_school)

# Curve B: vary students per within-cell
breaks_within  <- c(5, 7, 9, 11, 13, 15, 18, 20)
m_20schools    <- simr::extend(m0, along = "school", n = 20)
pc_within      <- simr::powerCurve(m_20schools, test = simr::fixed(int_term, "t"),
                                   within = "school+treat+mod",
                                   breaks = breaks_within, nsim = 200)
pc_within_tbl  <- pc_to_df(pc_within)

# Curve C: LRT (drop the interaction)
pc_lrt         <- simr::powerCurve(m_extended,
                                   test   = simr::fcompare(y ~ treat + mod + pre + (1 | school)),
                                   along  = "school", breaks = breaks_sch, nsim = 200)
pc_lrt_tbl     <- pc_to_df(pc_lrt)

# Export CSVs
write.csv(pc_school_tbl, "data/PowerCurve_Schools.csv",     row.names = FALSE)
write.csv(pc_within_tbl, "data/PowerCurve_Within.csv",      row.names = FALSE)
write.csv(pc_lrt_tbl,    "data/PowerCurve_Schools_LRT.csv", row.names = FALSE)
cat("Power curve CSVs saved to data/\n")
```

### 5.2 Power Curve Plots

```{r power-curve-plots, fig.width=7.5, fig.height=5}
# Helper to standardize column names across simr versions
prep_pc <- function(tbl, x_col) {
  names(tbl)[1] <- x_col
  tbl |>
    dplyr::mutate(
      power = dplyr::coalesce(
        if ("mean"  %in% names(tbl)) tbl[["mean"]]  else NULL,
        if ("y"     %in% names(tbl)) tbl[["y"]]     else NULL
      ),
      lwr = dplyr::coalesce(
        if ("lower" %in% names(tbl)) tbl[["lower"]] else NULL,
        if ("lwr"   %in% names(tbl)) tbl[["lwr"]]   else NULL
      ),
      upr = dplyr::coalesce(
        if ("upper" %in% names(tbl)) tbl[["upper"]] else NULL,
        if ("upr"   %in% names(tbl)) tbl[["upr"]]   else NULL
      )
    )
}

df_school <- prep_pc(pc_school_tbl, "num_schools")
df_within <- prep_pc(pc_within_tbl, "students_per_cell")

# Plot A: Power vs Number of Schools
p_school <- ggplot(df_school, aes(x = num_schools, y = power)) +
  geom_ribbon(aes(ymin = lwr, ymax = upr), fill = "#4F81BD", alpha = 0.2) +
  geom_line(color = "#1F497D", linewidth = 1.2) +
  geom_point(size = 2.5, color = "#1F497D") +
  geom_hline(yintercept = 0.80, linetype = "dashed", color = "gray50") +
  geom_hline(yintercept = 0.90, linetype = "dotted", color = "gray50") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits = c(0, 1)) +
  labs(
    title    = "Power vs. Number of Schools (Treatment × Moderator Interaction)",
    subtitle = "95% Monte Carlo CI shaded; dashed = 80% power, dotted = 90% power",
    x        = "Number of Schools",
    y        = "Estimated Power (1 − β)"
  ) +
  theme_bw(base_size = 13) +
  theme(panel.grid.minor  = element_blank(),
        panel.border      = element_rect(color = "black", fill = NA),
        plot.title        = element_text(face = "bold"),
        plot.background   = element_rect(fill = "white", color = NA),
        panel.background  = element_rect(fill = "white", color = NA))

ggsave("figures/PowerCurve_Schools_Workshop_White.png",
       p_school, width = 7.5, height = 5, dpi = 300)
print(p_school)

# Plot B: Power vs Students per Cell
p_within <- ggplot(df_within, aes(x = students_per_cell, y = power)) +
  geom_ribbon(aes(ymin = lwr, ymax = upr), fill = "#C55A11", alpha = 0.2) +
  geom_line(color = "#843C0C", linewidth = 1.2) +
  geom_point(size = 2.5, color = "#843C0C") +
  geom_hline(yintercept = 0.80, linetype = "dashed", color = "gray50") +
  geom_hline(yintercept = 0.90, linetype = "dotted", color = "gray50") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits = c(0, 1)) +
  labs(
    title    = "Power vs. Students per School × Treatment × Moderator Cell",
    subtitle = "95% Monte Carlo CI shaded; dashed = 80% power, dotted = 90% power",
    x        = "Students per School × Treatment × Moderator Cell",
    y        = "Estimated Power (1 − β)"
  ) +
  theme_bw(base_size = 13) +
  theme(panel.grid.minor  = element_blank(),
        panel.border      = element_rect(color = "black", fill = NA),
        plot.title        = element_text(face = "bold"),
        plot.background   = element_rect(fill = "white", color = NA),
        panel.background  = element_rect(fill = "white", color = NA))

ggsave("figures/PowerCurve_Within_Workshop_White.png",
       p_within, width = 7.5, height = 5, dpi = 300)
print(p_within)
cat("Power curve figures saved to figures/\n")
```

---

## 6. Simulation -- Mediation Power

This section estimates power to detect the **indirect (mediated) effect** via
bootstrap mediation analysis using the `mediation` package.

**Model:** Treatment → Mediator (a = 0.30) → Outcome (b = 0.35), with direct
effect c′ = 0.10. Power is the proportion of 300 replications in which the 95%
bootstrap CI for the indirect effect (a × b = 0.105) excludes zero.

```{r mediation-sim, message=FALSE, warning=FALSE}
set.seed(1234)

nsim_med  <- 300
boot_reps <- 1000
a_path    <- 0.30
b_path    <- 0.35
c_prime   <- 0.10

# Single mediation run: returns 1 if indirect effect CI excludes zero
sim_one_med <- function(N = planned_N) {
  Tt  <- rbinom(N, 1, 0.5)
  M   <- a_path * Tt + rnorm(N)
  Y   <- c_prime * Tt + b_path * M + rnorm(N)
  d   <- data.frame(Y, M, T = Tt)
  fit.M <- lm(M ~ T, data = d)
  fit.Y <- lm(Y ~ T + M, data = d)
  med   <- mediation::mediate(fit.M, fit.Y, treat = "T", mediator = "M",
                               boot = TRUE, sims = boot_reps)
  ci <- med$d0.ci
  as.numeric(!(ci[1] <= 0 & ci[2] >= 0))
}

res       <- replicate(nsim_med, sim_one_med())
power_med <- mean(res)

# Table B4
med_summary <- data.frame(
  `Path a`               = a_path,
  `Path b`               = b_path,
  `Indirect Effect (a×b)`= round(a_path * b_path, 3),
  `Direct Effect (c′)`   = c_prime,
  `Simulations`          = nsim_med,
  `Bootstraps`           = boot_reps,
  `Estimated Power (1–β)`= round(power_med, 2),
  check.names = FALSE
)

knitr::kable(
  med_summary,
  caption = "*Table B4.* Estimated power to detect the indirect effect via bootstrapped mediation analysis (N = 163; 300 simulations; 1,000 bootstraps per run).",
  align   = c("c","c","c","c","c","c","c"),
  digits  = 2
)
cat("\n*Note.* Power = proportion of simulations where the 95% bootstrap CI excludes zero.\n")
```

---

## 7. Analytic Power Curve

```{r analytic-power-curve, fig.width=8, fig.height=5.5}
n_eff      <- planned_N / DE_planned
n_per_grp  <- n_eff / 2
d_vals     <- seq(0.20, 0.90, by = 0.01)

power_vals <- sapply(d_vals, \(d)
  pwr::pwr.t.test(n = n_per_grp, d = d, sig.level = alpha,
                  type = "two.sample", alternative = "two.sided")$power)

df_curve <- data.frame(d = d_vals, power = power_vals)
bm_power <- df_curve$power[which.min(abs(df_curve$d - 0.55))]

ggplot(df_curve, aes(x = d, y = power)) +
  geom_line(color = "#1F497D", linewidth = 1.2) +
  geom_point(aes(x = 0.55, y = bm_power), color = "#1F497D", size = 3) +
  geom_hline(yintercept = 0.80, linetype = "dashed", color = "gray40") +
  geom_vline(xintercept = 0.55, linetype = "dashed", color = "#1F497D", alpha = 0.6) +
  annotate("text", x = 0.57, y = 0.10,
           label = paste0("d = 0.55\nPower = ", round(bm_power, 2)),
           hjust = 0, size = 3.5, color = "#1F497D") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits = c(0, 1)) +
  labs(
    title    = "Analytic Power Curve -- Two-Sample t-Test",
    subtitle = paste0("N = ", planned_N, "; DE = ", DE_planned,
                      "; Effective N ≈ ", round(n_eff)),
    x        = "Standardized Effect Size (Cohen's d)",
    y        = "Statistical Power (1 − β)",
    caption  = paste0(
      "Dashed lines mark 80% power and the benchmark effect size (d = 0.55).\n",
      "Effective sample size accounts for clustering (Design Effect = ", DE_planned, ")."
    )
  ) +
  theme_bw(base_size = 13) +
  theme(panel.grid.minor = element_blank(),
        panel.border     = element_rect(color = "black", fill = NA),
        plot.title       = element_text(face = "bold", size = 12),
        plot.caption     = element_text(hjust = 0, size = 10,
                                        margin = margin(t = 10)))
```

---

## 8. Export All Tables

```{r export-all-tables}
tables <- list(
  list(name = "Table_B0_Helper_Functions",
       df   = helper_table,
       cap  = "Table B0. Summary of Helper Functions for Power Analysis"),
  list(name = "Table_B1_RequiredN_Benchmark",
       df   = table_requiredN,
       cap  = "Table B1. Required N for d = 0.55 at 80% Power"),
  list(name = "Table_B2_Sensitivity_Analysis",
       df   = sensitivity,
       cap  = "Table B2. Power and MDE for N = 163, DE = 1.56"),
  list(name = "Table_B3_Moderation_Power",
       df   = power_summary,
       cap  = "Table B3. Moderation Power (Treatment × Moderator, N = 163)"),
  list(name = "Table_B4_Mediation_Power",
       df   = med_summary,
       cap  = "Table B4. Mediation Power (N = 163, 300 simulations)")
)

# Word (.docx)
doc <- officer::read_docx()
for (tb in tables) {
  doc <- officer::body_add_par(doc, tb$cap, style = "heading 2") |>
    flextable::body_add_flextable(flextable::autofit(flextable::qflextable(tb$df))) |>
    officer::body_add_par("")
}
print(doc, target = "tables/REP_Power_Tables.docx")

# Excel (.xlsx)
sheets <- stats::setNames(lapply(tables, `[[`, "df"),
                          sapply(tables, `[[`, "name"))
writexl::write_xlsx(sheets, path = "tables/REP_Power_Tables.xlsx")

# PNGs via gt
for (tb in tables) {
  gt::gt(tb$df) |>
    gt::tab_header(title = tb$cap) |>
    gt::gtsave(filename = file.path("figures", paste0(tb$name, ".png")))
}

cat("All tables exported to tables/ and figures/\n")
```

---

## 9. Session Info

```{r session-info}
cat("Last run:", format(Sys.time(), "%Y-%m-%d %H:%M:%S %Z"), "\n\n")
sessionInfo()
if (requireNamespace("renv", quietly = TRUE)) suppressMessages(renv::status())
```
