---
title: "REP 3.1 Fidelity Measures"
author: "WCER School Mental Health Collaborative"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_notebook:
    df_print: paged
    highlight: tango
    number_sections: yes
    theme: flatly
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
  html_document:
    df_print: paged
    highlight: tango
    number_sections: yes
    theme: flatly
    toc: yes
    toc_float: yes
---

## Overview

This notebook computes fidelity metrics for three REP 3.1 intervention components:
**CICO** (Check-In Check-Out, across AM / Daytime / PM delivery formats),
**CBI** (Curriculum-Based Instruction), and **RF** (Resilient Families, across
three meeting protocols).

For each component, the notebook calculates adherence and quality percentages,
standard deviations, and min/max values per fidelity item, as well as program-wide
overall scores. A parallel exposure analysis computes the proportion of total
observation opportunities that were actually observed.

> **Note on data:** School names and all implementer/observer names have been
> anonymized. Schools are coded School_A through School_E. Implementers and
> observers are coded Implementer_A/B/... and Observer_A/B/... using a consistent
> mapping dictionary applied to the source data.

---

## 1. Setup

```{r setup, message=FALSE, warning=FALSE}
packages <- c("readxl", "tidyverse", "writexl", "purrr")
new_packages <- setdiff(packages, installed.packages()[, "Package"])
if (length(new_packages)) install.packages(new_packages, quiet = TRUE)
invisible(lapply(packages, library, character.only = TRUE))

excel_file <- "data/REP2_Synthetic.xlsx"
```

---

## 2. Load Data

### 2.1 CICO

Sheet names use anonymized school codes (School_A through School_E).

```{r load-cico, warning=FALSE}
# Column selections per delivery format
columns_cico_am <- c(1, 4, 8, 9:13, 17:29)
columns_cico_dt <- c(1, 4, 8:20)
columns_cico_pm <- c(1, 4, 8:26)

sheet_names_am <- c("School_A AM", "School_B AM", "School_C AM",
                    "School_D AM", "School_E AM")
sheet_names_dt <- c("School_A DT", "School_B DT", "School_C DT",
                    "School_D DT", "School_E DT")
sheet_names_pm <- c("School_A PM", "School_B PM", "School_C PM",
                    "School_D PM", "School_E PM")

# Shared import function: select columns, recode Yes/No/NA, drop all-NA rows
read_cico_sheet <- function(sheet_name, columns_to_select) {
  read_excel(excel_file, sheet = sheet_name) |>
    select(all_of(columns_to_select)) |>
    mutate(across(everything(), as.character)) |>
    mutate(across(everything(), ~ case_when(
      . == "Yes (1)"            ~ "1",
      . == "No (0)"             ~ "0",
      . %in% c("N/A", "n/a")   ~ NA_character_,
      TRUE                      ~ .
    ))) |>
    filter(!if_all(everything(), is.na))
}

cico_am <- bind_rows(lapply(sheet_names_am, read_cico_sheet,
                             columns_to_select = columns_cico_am))
cico_dt <- bind_rows(lapply(sheet_names_dt, read_cico_sheet,
                             columns_to_select = columns_cico_dt))
cico_pm <- bind_rows(lapply(sheet_names_pm, read_cico_sheet,
                             columns_to_select = columns_cico_pm))

cat("CICO rows -- AM:", nrow(cico_am), "| DT:", nrow(cico_dt),
    "| PM:", nrow(cico_pm), "\n")
```

### 2.2 CBI

```{r load-cbi}
cbi <- read_excel(excel_file, sheet = "CBI Lessons") |>
  slice(-1) |>                   # drop label row
  select(1, 4:58) |>
  mutate(across(2:last_col(), ~ {
    . <- gsub("Yes \\(1\\)", "1", .)
    . <- gsub("No \\(0\\)",  "0", .)
    suppressWarnings(as.numeric(.))
  }))

# Recode school name column to anonymized labels
cbi <- cbi |>
  mutate(across(1, ~ recode(.,
    "Blackhawk"                  = "School_A",
    "Blackhawk Middle School"    = "School_A",
    "Black Hawk"                 = "School_A",
    "Olson Elementary"           = "School_C",
    "Spring Harbor Middle School"= "School_E",
    "Spring Harbor"              = "School_E",
    "Gompers"                    = "School_B",
    "Schenk"                     = "School_D"
  )))

cat("CBI rows:", nrow(cbi), "\n")
```

### 2.3 RF

```{r load-rf, warning=FALSE}
read_rf_sheet <- function(sheet_name) {
  read_excel(excel_file, sheet = sheet_name) |>
    slice(-1) |>
    mutate(across(everything(), as.character)) |>
    mutate(across(everything(), ~ case_when(
      . == "Yes (1)"            ~ "1",
      . == "No (0)"             ~ "0",
      . %in% c("N/A", "n/a")   ~ NA_character_,
      TRUE                      ~ .
    ))) |>
    filter(!if_all(everything(), is.na))
}

rf_meeting_1 <- read_rf_sheet("RF Meeting 1")
rf_meeting_2 <- read_rf_sheet("RF Meeting 2")
rf_meeting_3 <- read_rf_sheet("RF Meeting 3") |>
  select(-last_col())    # drop trailing empty column

cat("RF rows -- M1:", nrow(rf_meeting_1), "| M2:", nrow(rf_meeting_2),
    "| M3:", nrow(rf_meeting_3), "\n")
```

---

## 3. Fidelity Metrics

A single shared function handles all metric calculations. Adherence and quality
items are identified by column name prefix (`S` = adherence steps, `Q` = quality
indicators). For RF, all columns are treated as adherence items.

```{r metrics-function}
#' Calculate per-column and overall fidelity metrics.
#' @param data        Data frame of numeric fidelity items (0/1/NA).
#' @param n_total     Total observation opportunities (typically nrow of the
#'                    full dataset before any column selection).
#' @param adj_cols    Optional named list: column names -> integer adjustments
#'                    to subtract from n_total (for items with fewer opportunities).
#' @param label       String label added to the final tibble.
calculate_fidelity <- function(data, n_total, adj_cols = list(), label = "") {
  data <- data |> mutate(across(everything(), ~ suppressWarnings(as.numeric(.))))

  adjusted_n <- sapply(colnames(data), function(cn) {
    adj <- adj_cols[[cn]]
    as.integer(n_total - if (!is.null(adj)) adj else 0L)
  })

  per_col <- tibble(
    Item              = colnames(data),
    N_Opportunities   = adjusted_n,
    N_Observed        = map_int(data, ~ sum(!is.na(.))),
    Pct_Adherence_Obs = map_dbl(data, ~ mean(. == 1, na.rm = TRUE) * 100),
    Pct_Adherence_Tot = map2_dbl(data, adjusted_n,
                                 ~ sum(.x == 1, na.rm = TRUE) / .y * 100),
    SD                = map_dbl(data, ~ sd(., na.rm = TRUE)),
    Min               = map_dbl(data, ~ min(., na.rm = TRUE)),
    Max               = map_dbl(data, ~ max(., na.rm = TRUE)),
    Label             = label
  )

  overall <- per_col |>
    summarise(
      Item              = paste("Overall", label),
      N_Opportunities   = sum(N_Opportunities),
      N_Observed        = sum(N_Observed),
      Pct_Adherence_Obs = mean(Pct_Adherence_Obs, na.rm = TRUE),
      Pct_Adherence_Tot = mean(Pct_Adherence_Tot, na.rm = TRUE),
      SD                = mean(SD, na.rm = TRUE),
      Min               = min(Min, na.rm = TRUE),
      Max               = max(Max, na.rm = TRUE),
      Label             = label
    )

  bind_rows(per_col, overall)
}
```

### 3.1 CICO -- AM

```{r cico-am-metrics}
adh_am <- cico_am |> select(starts_with("S")) |>
  mutate(across(everything(), ~ suppressWarnings(as.numeric(.))))
qua_am <- cico_am |> select(starts_with("Q")) |>
  mutate(across(everything(), ~ suppressWarnings(as.numeric(.))))

# Columns 5-17 have 3 fewer opportunities; columns 18-19 have 12 fewer
col_names_am <- colnames(adh_am)
adj_am <- setNames(
  c(rep(3L, length(col_names_am[5:min(17, length(col_names_am))])),
    rep(12L, length(col_names_am[18:min(19, length(col_names_am))]))),
  c(col_names_am[5:min(17, length(col_names_am))],
    col_names_am[18:min(19, length(col_names_am))])
)

final_cico_am <- bind_rows(
  calculate_fidelity(adh_am, nrow(cico_am), adj_cols = adj_am, label = "Adherence"),
  calculate_fidelity(qua_am, nrow(cico_am), label = "Quality")
)
print(final_cico_am)
```

### 3.2 CICO -- Daytime

```{r cico-dt-metrics}
adh_dt <- cico_dt |> select(starts_with("S")) |>
  mutate(across(everything(), ~ suppressWarnings(as.numeric(.))))
qua_dt <- cico_dt |> select(starts_with("Q")) |>
  mutate(across(everything(), ~ suppressWarnings(as.numeric(.))))

# First 5 adherence columns have 9 fewer opportunities
adj_dt <- setNames(rep(9L, min(5, ncol(adh_dt))),
                   colnames(adh_dt)[1:min(5, ncol(adh_dt))])

final_cico_dt <- bind_rows(
  calculate_fidelity(adh_dt, nrow(cico_dt), adj_cols = adj_dt, label = "Adherence"),
  calculate_fidelity(qua_dt, nrow(cico_dt), label = "Quality")
)
print(final_cico_dt)
```

### 3.3 CICO -- PM

```{r cico-pm-metrics}
adh_pm <- cico_pm |> select(starts_with("S")) |>
  mutate(across(everything(), ~ suppressWarnings(as.numeric(.))))
qua_pm <- cico_pm |> select(starts_with("Q")) |>
  mutate(across(everything(), ~ suppressWarnings(as.numeric(.))))

# Columns 4-19 have 2 fewer opportunities
col_names_pm <- colnames(adh_pm)
adj_pm <- setNames(rep(2L, length(col_names_pm[4:min(19, length(col_names_pm))])),
                   col_names_pm[4:min(19, length(col_names_pm))])

final_cico_pm <- bind_rows(
  calculate_fidelity(adh_pm, nrow(cico_pm), adj_cols = adj_pm, label = "Adherence"),
  calculate_fidelity(qua_pm, nrow(cico_pm), label = "Quality")
)
print(final_cico_pm)
```

### 3.4 CICO Overall Summary

```{r cico-summary}
bind_rows(
  final_cico_am |> filter(startsWith(Item, "Overall")) |> mutate(Format = "AM"),
  final_cico_dt |> filter(startsWith(Item, "Overall")) |> mutate(Format = "DT"),
  final_cico_pm |> filter(startsWith(Item, "Overall")) |> mutate(Format = "PM")
)
```

### 3.5 CBI

```{r cbi-metrics}
adh_cbi <- cbi |> select(starts_with("S")) |>
  mutate(across(everything(), ~ suppressWarnings(as.numeric(.))))
qua_cbi <- cbi |> select(starts_with("Q")) |>
  select(-any_of("Q3")) |>       # Q3 is the school label column, not a fidelity item
  mutate(across(everything(), ~ suppressWarnings(as.numeric(.))))

final_cbi <- bind_rows(
  calculate_fidelity(adh_cbi, nrow(cbi), label = "Adherence"),
  calculate_fidelity(qua_cbi, nrow(cbi), label = "Quality")
)
print(final_cbi)
```

### 3.6 RF -- Meetings 1, 2, 3

```{r rf-metrics}
final_rf_1 <- calculate_fidelity(
  rf_meeting_1 |> mutate(across(everything(), ~ suppressWarnings(as.numeric(.)))),
  nrow(rf_meeting_1), label = "Adherence"
)

final_rf_2 <- calculate_fidelity(
  rf_meeting_2 |> mutate(across(everything(), ~ suppressWarnings(as.numeric(.)))),
  nrow(rf_meeting_2), label = "Adherence"
)

final_rf_3 <- calculate_fidelity(
  rf_meeting_3 |> mutate(across(everything(), ~ suppressWarnings(as.numeric(.)))),
  nrow(rf_meeting_3), label = "Adherence"
)

# Overall RF summary
bind_rows(
  final_rf_1 |> filter(startsWith(Item, "Overall")) |> mutate(Meeting = "RF Meeting 1"),
  final_rf_2 |> filter(startsWith(Item, "Overall")) |> mutate(Meeting = "RF Meeting 2"),
  final_rf_3 |> filter(startsWith(Item, "Overall")) |> mutate(Meeting = "RF Meeting 3")
)
```

---

## 4. Exposure Analysis

Exposure quantifies the proportion of total observation opportunities that were
actually covered (non-NA) for each student-school combination.

```{r exposure-function}
#' Compute exposure percentages by grouping variable.
#' @param data       Data frame.
#' @param item_cols  Character vector of column names to include.
#' @param group_col  Optional grouping column name (NULL = overall only).
compute_exposure <- function(data, item_cols, group_col = NULL) {
  df <- data |>
    rowwise() |>
    mutate(
      total = length(c_across(all_of(item_cols))),
      observed = sum(!is.na(c_across(all_of(item_cols))))
    ) |>
    ungroup()

  if (!is.null(group_col)) {
    df <- df |>
      group_by(across(all_of(group_col))) |>
      summarise(
        total_potential = sum(total),
        observed_exposures = sum(observed),
        exposure_pct = observed_exposures / total_potential * 100,
        .groups = "drop"
      ) |>
      filter(total_potential > 0)
  } else {
    df <- df |>
      summarise(
        total_potential = sum(total),
        observed_exposures = sum(observed),
        exposure_pct = observed_exposures / total_potential * 100
      )
  }
  df
}
```

### 4.1 CICO Exposure

```{r cico-exposure}
cico_items <- function(df) grep("^(S|Q)", names(df), value = TRUE)

# Student-level (grouped by anonymized Student Name + School)
exp_am_student <- compute_exposure(cico_am, cico_items(cico_am),
                                   group_col = c("Student Name", "School"))
exp_dt_student <- compute_exposure(cico_dt, cico_items(cico_dt),
                                   group_col = c("Student Name", "School"))
exp_pm_student <- compute_exposure(cico_pm, cico_items(cico_pm),
                                   group_col = c("Student Name", "School"))

# Overall per format
overall_am <- compute_exposure(cico_am, cico_items(cico_am))
overall_dt <- compute_exposure(cico_dt, cico_items(cico_dt))
overall_pm <- compute_exposure(cico_pm, cico_items(cico_pm))

# Combined CICO overall
cico_overall <- bind_rows(overall_am, overall_dt, overall_pm) |>
  summarise(
    total_potential    = sum(total_potential),
    observed_exposures = sum(observed_exposures),
    exposure_pct       = observed_exposures / total_potential * 100
  )
cat("CICO overall exposure:", round(cico_overall$exposure_pct, 1), "%\n")
```

### 4.2 CBI Exposure

```{r cbi-exposure}
cbi_items <- setdiff(grep("^(S|Q)", names(cbi), value = TRUE), "Q3")
exp_cbi_school  <- compute_exposure(cbi, cbi_items, group_col = "Q3")
overall_cbi     <- compute_exposure(cbi, cbi_items)
cat("CBI overall exposure:", round(overall_cbi$exposure_pct, 1), "%\n")
print(exp_cbi_school)
```

### 4.3 RF Exposure

```{r rf-exposure}
rf_overall_1 <- compute_exposure(rf_meeting_1, names(rf_meeting_1))
rf_overall_2 <- compute_exposure(rf_meeting_2, names(rf_meeting_2))
rf_overall_3 <- compute_exposure(rf_meeting_3, names(rf_meeting_3))

aggregated_rf <- bind_rows(rf_overall_1, rf_overall_2, rf_overall_3) |>
  summarise(
    total_potential    = sum(total_potential),
    observed_exposures = sum(observed_exposures),
    exposure_pct       = observed_exposures / total_potential * 100
  )
cat("RF overall exposure:", round(aggregated_rf$exposure_pct, 1), "%\n")
```

### 4.4 All Components Combined

```{r all-exposure}
all_combined <- bind_rows(aggregated_rf, overall_cbi, cico_overall) |>
  summarise(
    total_potential    = sum(total_potential),
    observed_exposures = sum(observed_exposures),
    exposure_pct       = observed_exposures / total_potential * 100
  )
cat("Overall exposure across all components:", round(all_combined$exposure_pct, 1), "%\n")
```

---

## 5. Export

```{r export}
# Fidelity metrics
write_xlsx(
  list(
    "CICO AM"       = final_cico_am,
    "CICO Daytime"  = final_cico_dt,
    "CICO PM"       = final_cico_pm,
    "CBI Lessons"   = final_cbi,
    "RF Meeting 1"  = final_rf_1,
    "RF Meeting 2"  = final_rf_2,
    "RF Meeting 3"  = final_rf_3
  ),
  path = "outputs/REP_Fidelity_Measures.xlsx"
)

# Exposure results
write_xlsx(
  list(
    "CICO AM - Student"          = exp_am_student,
    "CICO DT - Student"          = exp_dt_student,
    "CICO PM - Student"          = exp_pm_student,
    "CICO AM - Overall"          = overall_am,
    "CICO DT - Overall"          = overall_dt,
    "CICO PM - Overall"          = overall_pm,
    "CICO - Overall"             = cico_overall,
    "CBI - School"               = exp_cbi_school,
    "CBI - Overall"              = overall_cbi,
    "Aggregated RF Results"      = aggregated_rf,
    "RF Meeting 1 - Overall"     = rf_overall_1,
    "RF Meeting 2 - Overall"     = rf_overall_2,
    "RF Meeting 3 - Overall"     = rf_overall_3,
    "All Combined Results"       = all_combined
  ),
  path = "outputs/rep_exposure.xlsx"
)

cat("Outputs saved to outputs/\n")
```

---

## 6. Session Info

```{r session-info}
sessionInfo()
```
