---
title: "REP 3.1 Analyses -- Descriptive Statistics, Imputation, and ANCOVA Models"
author: "WCER School Mental Health Collaborative"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_notebook:
    df_print: paged
    highlight: tango
    number_sections: yes
    theme: flatly
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
  html_document:
    df_print: paged
    highlight: tango
    number_sections: yes
    theme: flatly
    toc: yes
    toc_float: yes
---

## Overview

This notebook contains the primary outcome analyses for the REP 3.1 component
analysis study. The workflow is:

1. Import and clean the student-level data
2. Parse and recode SRCS ratio fields, demographics, and condition assignment
3. Produce descriptive statistics tables (overall and by condition) exported to Word
4. Select the best multiple imputation predictor set for each outcome via RMSE
5. Impute missing values using MICE
6. Fit ANCOVA models (Post ~ Pre + Condition) for all outcomes
7. Compute Cohen's d effect sizes for every coefficient
8. Produce a formatted regression results table

**Outcomes:** BESST (teacher/student empathy), BFS (behavior/feelings), YSR
(youth self-report internalizing), PCOISS (parental confidence), CASSS (social
support from classmates/teachers), SRCS (school readiness composite)

**Conditions:**
- Condition 1: CBI + CICO
- Condition 2: CBI + RF
- Condition 3: CBI + CICO + RF (reference = Condition 1)

> **Note on data:** School names are anonymized to School_A through School_E.
> The source data file is not included in this repository. Update the
> `excel_file` path in the Setup chunk to point to your local copy before
> running.

---

## 1. Setup

```{r setup, message=FALSE, warning=FALSE}
packages <- c("readxl", "tidyverse", "ggplot2", "stringr", "purrr",
              "mice", "corrr", "knitr", "broom", "kableExtra",
              "lubridate", "survey", "officer", "emmeans")
new_packages <- setdiff(packages, installed.packages()[, "Package"])
if (length(new_packages)) install.packages(new_packages, quiet = TRUE)
invisible(lapply(packages, library, character.only = TRUE))

# Update this path to point to your local data file
excel_file <- "data/REP_3.1_Data_Spreadsheet.xlsx"
d <- read_excel(excel_file, col_types = "guess")

cat("Rows:", nrow(d), "| Columns:", ncol(d), "\n")
```

---

## 2. Data Cleaning and Recoding

### 2.1 SRCS Pre/Post (ratio string to two numeric components)

The SRCS variable is stored as a string like `"45 (s-1) 32 (s-2)"`. This chunk
extracts the two subscale scores into separate numeric columns.

```{r srcs-parse}
split_srcs <- function(x) {
  if (is.na(x) || x %in% c("", "missing")) return(c(NA_real_, NA_real_))
  s1 <- as.numeric(str_extract(x, "\\d+(?=\\s*\\(s-1\\))"))
  s2 <- as.numeric(str_extract(x, "\\d+(?=\\s*\\(s-2\\))"))
  c(s1, s2)
}

d <- d |>
  mutate(
    split_pre  = lapply(SRCS_Pre,  split_srcs),
    split_post = lapply(SRCS_Post, split_srcs),
    SRCS_Pre_s1  = map_dbl(split_pre,  1),
    SRCS_Pre_s2  = map_dbl(split_pre,  2),
    SRCS_Post_s1 = map_dbl(split_post, 1),
    SRCS_Post_s2 = map_dbl(split_post, 2)
  ) |>
  select(-split_pre, -split_post)

head(d |> select(SRCS_Pre, SRCS_Pre_s1, SRCS_Pre_s2,
                  SRCS_Post, SRCS_Post_s1, SRCS_Post_s2))
```

### 2.2 Gender

```{r gender-recode}
gender_labels <- c("1" = "Male", "2" = "Female", "3" = "Non-binary / Third gender",
                   "4" = "Prefer to self-describe", "5" = "Prefer not to say")

d <- d |>
  mutate(Gender = recode(as.character(Gender), !!!gender_labels))

d |> count(Gender) |> mutate(pct = round(n / sum(n) * 100, 1))
```

### 2.3 Student Participation

```{r participation-recode}
participation_labels <- c(
  "1" = "Full Participation",
  "2" = "Partial Participation",
  "3" = "Minimal Participation"
)

d <- d |>
  mutate(
    Student_Participation  = recode(as.character(`Student Participation`),
                                    !!!participation_labels),
    Student_Participation2 = as.numeric(`Student Participation`)
  )

d |> count(Student_Participation) |> mutate(pct = round(n / sum(n) * 100, 1))
```

### 2.4 Condition

```{r condition-recode}
d <- d |>
  mutate(Condition = case_when(
    Condition == 1 ~ "CBI, CICO",
    Condition == 2 ~ "CBI, RF",
    Condition == 3 ~ "CBI, CICO, RF",
    TRUE           ~ NA_character_
  ))

d |> count(Condition) |> mutate(pct = round(n / sum(n) * 100, 1))
```

### 2.5 School (anonymized)

Real school names are replaced with coded labels at load time to protect
participating site identities.

```{r school-recode}
school_map <- c(
  "Black Hawk"                   = "School_A",
  "Black Hawk Middle School"     = "School_A",
  "Blackhawk"                    = "School_A",
  "Blackhawk Middle School"      = "School_A",
  "Gompers"                      = "School_B",
  "Olson"                        = "School_C",
  "Olson Elementary"             = "School_C",
  "Schenk"                       = "School_D",
  "Spring Harbor"                = "School_E",
  "Spring Harbor Middle School"  = "School_E"
)

d <- d |>
  mutate(School = recode(School, !!!school_map))

d |> count(School) |> mutate(pct = round(n / sum(n) * 100, 1))
```

### 2.6 Race/Ethnicity

```{r race-recode}
race_labels <- c(
  "1" = "American Indian / Alaska Native",
  "2" = "Asian",
  "3" = "Black / African American",
  "4" = "Hispanic / Latino",
  "5" = "Native Hawaiian / Pacific Islander",
  "6" = "White",
  "7" = "Two or more races",
  "8" = "Other",
  "9" = "Prefer not to say"
)

d <- d |>
  mutate(RaceEthnicity = recode(as.character(RaceEthnicity), !!!race_labels))

d |> count(RaceEthnicity) |> mutate(pct = round(n / sum(n) * 100, 1))
```

### 2.7 Date of Birth / Age

```{r age}
d <- d |>
  mutate(
    DOB = case_when(
      is.na(DOB) | DOB == "unknown" ~ NA_character_,
      TRUE ~ as.character(DOB)
    ),
    DOB = parse_date_time(DOB, orders = c("mdy", "ymd", "dmy")),
    Age = as.numeric(difftime(Sys.Date(), DOB, units = "days")) / 365.25
  )

d |>
  summarise(
    N     = sum(!is.na(Age)),
    Mean  = round(mean(Age, na.rm = TRUE), 1),
    SD    = round(sd(Age, na.rm = TRUE), 1),
    Min   = round(min(Age, na.rm = TRUE), 1),
    Q1    = round(quantile(Age, .25, na.rm = TRUE), 1),
    Median= round(median(Age, na.rm = TRUE), 1),
    Q3    = round(quantile(Age, .75, na.rm = TRUE), 1),
    Max   = round(max(Age, na.rm = TRUE), 1)
  )
```

---

## 3. Descriptive Statistics

### 3.1 Overall Sample

```{r desc-overall}
d_design <- svydesign(id = ~1, data = d, weights = NULL)

categorical_vars <- c("Student_Participation", "School", "Condition",
                       "Gender", "RaceEthnicity")

continuous_vars <- c(
  "BESST_Pre_ERI", "BESST_Pre_IRI", "BESST_Pre_ARI", "BESST_Pre_BERI",
  "BESST_Post_ERI", "BESST_Post_IRI", "BESST_Post_ARI", "BESST_Post_BERI",
  "BESSP_Pre_ERI", "BESSP_Pre_IRI", "BESSP_Pre_ARI", "BESSP_Pre_BERI",
  "BESSP_Post_ERI", "BESSP_Post_IRI", "BESSP_Post_ARI", "BESSP_Post_BERI",
  "BFSs_Pre_INT", "BFSs_Pre_EXT", "BFSs_Pre_TOT",
  "BFSc_Pre_INT", "BFSc_Pre_EXT", "BFSc_Pre_TOT",
  "BFSc_Post_INT", "BFSc_Post_EXT", "BFSc_Post_TOT",
  "YSR_Pre_INT", "YSR_Post_INT",
  "PCOISS_Pre", "PCOISS_Post",
  "CASSS_C_Pre", "CASSS_T_Pre", "CASSS_C_Post", "CASSS_T_Post",
  "BFSs_Post_INT", "BFSs_Post_EXT", "BFSs_Post_TOT",
  "SRCS_Pre_s1", "SRCS_Pre_s2", "SRCS_Post_s1", "SRCS_Post_s2"
)

# Categorical frequency table
calc_pct <- function(var) {
  prop <- svytable(as.formula(paste("~", var)), d_design)
  data.frame(
    Variable   = var,
    Level      = names(prop),
    Count      = as.numeric(prop),
    Percentage = round(as.numeric(prop / sum(prop) * 100), 2)
  ) |> arrange(desc(Count))
}

categorical_summary <- bind_rows(lapply(categorical_vars, calc_pct))

# Continuous summary
calc_cont <- function(var, design) {
  x <- na.omit(design$variables[[var]])
  data.frame(
    Variable = var, N = length(x),
    Mean = round(mean(x), 2), SD = round(sd(x), 2),
    Min = round(min(x), 2), Q1 = round(quantile(x, .25), 2),
    Median = round(median(x), 2), Q3 = round(quantile(x, .75), 2),
    Max = round(max(x), 2)
  )
}

continuous_summary <- bind_rows(
  lapply(intersect(continuous_vars, names(d)), calc_cont, design = d_design)
)

# Export to Word
doc <- read_docx() |>
  body_add_par("Descriptive Statistics Report", style = "heading 1") |>
  body_add_par("Categorical Variables", style = "heading 2") |>
  body_add_table(categorical_summary) |>
  body_add_par("Continuous Variables", style = "heading 2") |>
  body_add_table(continuous_summary)
print(doc, target = "outputs/Descriptive_Statistics_Report.docx")
cat("Saved: outputs/Descriptive_Statistics_Report.docx\n")
```

### 3.2 By Condition

```{r desc-by-condition}
calc_cont_by_cond <- function(var, design) {
  results <- lapply(unique(na.omit(d$Condition)), function(cond) {
    x <- na.omit(design$variables[[var]][d$Condition == cond])
    data.frame(
      Variable = var, Condition = cond, N = length(x),
      Q1 = round(quantile(x, .25), 2), Mean = round(mean(x), 2),
      Median = round(median(x), 2), Q3 = round(quantile(x, .75), 2),
      Min = round(min(x), 2), Max = round(max(x), 2)
    )
  })
  bind_rows(results)
}

continuous_by_cond <- bind_rows(
  lapply(intersect(continuous_vars, names(d)), calc_cont_by_cond, design = d_design)
)

doc2 <- read_docx() |>
  body_add_par("Descriptive Statistics by Condition", style = "heading 1") |>
  body_add_par("Continuous Variables", style = "heading 2") |>
  body_add_table(continuous_by_cond)
print(doc2, target = "outputs/Descriptive_Statistics_Report_Condition.docx")
cat("Saved: outputs/Descriptive_Statistics_Report_Condition.docx\n")
```

---

## 4. Multiple Imputation

### 4.1 Imputation predictor selection via RMSE

For each outcome, we search over combinations of up to 3 predictors and select
the set that minimizes RMSE on 10% of artificially masked values.

```{r imputation-setup}
# Base dataset for imputation modelling
data <- d |>
  select(
    BESST_Post_IRI, BESST_Pre_IRI,
    BFSs_Post_INT,  BFSs_Pre_INT,
    YSR_Post_INT,   YSR_Pre_INT,
    PCOISS_Post,    PCOISS_Pre,
    CASSS_C_Post,   CASSS_C_Pre,
    CASSS_T_Post,   CASSS_T_Pre,
    SRCS_Pre_s1, SRCS_Pre_s2, SRCS_Post_s1, SRCS_Post_s2,
    Condition, Gender,
    BESSP_Pre_IRI, BESSP_Post_IRI,
    Student_Participation, Student_Participation2
  ) |>
  mutate(
    Gender                = as.factor(Gender),
    Condition             = as.factor(Condition),
    Student_Participation = as.factor(Student_Participation)
  )

# Shared helpers
generate_combinations <- function(predictors, min_size, max_size) {
  combs <- list()
  for (size in min_size:max_size)
    combs <- c(combs, lapply(combn(predictors, size, simplify = FALSE),
                             paste, collapse = ", "))
  combs
}

calculate_rmse <- function(original, imputed)
  sqrt(mean((original - imputed)^2, na.rm = TRUE))

run_rmse <- function(data, dv, predictor_sets) {
  results <- sapply(names(predictor_sets), function(sn) {
    preds <- predictor_sets[[sn]]
    ds <- data |> select(all_of(c(preds, dv)))
    set.seed(123)
    idx <- sample(seq_len(nrow(ds)), floor(0.1 * nrow(ds)))
    ds[[dv]][idx] <- NA
    imp <- mice(ds, m = 5, method = "pmm", seed = 123, printFlag = FALSE)
    comp <- complete(imp)
    calculate_rmse(data[[dv]][idx], comp[[dv]][idx])
  })
  tibble(Set = names(results), RMSE = results)
}

build_sets <- function(predictors) {
  base <- as.list(setNames(as.list(predictors), paste0("set", seq_along(predictors))))
  combs <- generate_combinations(predictors, 2, 3)
  extra <- lapply(combs, \(x) strsplit(x, ", ")[[1]])
  extra_named <- setNames(extra, paste0("set", seq(length(base) + 1,
                                                    length(base) + length(extra))))
  c(base, extra_named)
}
```

```{r impute-besst, warning=FALSE, message=FALSE}
preds_besst <- c("Gender", "BESSP_Pre_IRI", "BFSs_Pre_INT", "PCOISS_Pre",
                  "CASSS_C_Pre", "CASSS_T_Pre", "Student_Participation",
                  "YSR_Pre_INT", "SRCS_Pre_s1", "SRCS_Pre_s2")
sets_besst  <- build_sets(preds_besst)
rmse_besst  <- run_rmse(data, "BESST_Pre_IRI", sets_besst)
best_besst  <- sets_besst[[rmse_besst$Set[which.min(rmse_besst$RMSE)]]]
cat("Best BESST predictors:", paste(best_besst, collapse = ", "), "\n")

imp_besst <- mice(data |> select(all_of(c(best_besst, "BESST_Pre_IRI"))),
                  m = 5, method = "pmm", seed = 123, printFlag = FALSE)
data <- data |>
  mutate(Imputed_BESST_Pre_IRI = ifelse(
    is.na(BESST_Pre_IRI), complete(imp_besst)$BESST_Pre_IRI, BESST_Pre_IRI))
```

```{r impute-all-outcomes, warning=FALSE, message=FALSE}
# Helper: impute one variable given best predictor set
impute_var <- function(data, dv, predictors) {
  preds <- build_sets(predictors)
  rmse  <- run_rmse(data, dv, preds)
  best  <- preds[[rmse$Set[which.min(rmse$RMSE)]]]
  cat(dv, "-- best predictors:", paste(best, collapse = ", "), "\n")
  imp <- mice(data |> select(all_of(c(best, dv))),
              m = 5, method = "pmm", seed = 123, printFlag = FALSE)
  list(data = data |> mutate(
    !!paste0("Imputed_", dv) := ifelse(
      is.na(.data[[dv]]), complete(imp)[[dv]], .data[[dv]])
  ), best_predictors = best)
}

shared_preds <- c("Gender", "BFSs_Pre_INT", "PCOISS_Pre", "CASSS_C_Pre",
                   "CASSS_T_Pre", "Student_Participation", "SRCS_Pre_s1",
                   "SRCS_Pre_s2", "BESSP_Pre_IRI", "BESST_Pre_IRI")

for (dv in c("BFSs_Pre_INT", "YSR_Pre_INT", "PCOISS_Pre",
             "CASSS_C_Pre", "CASSS_T_Pre",
             "BESST_Post_IRI", "BFSs_Post_INT", "YSR_Post_INT",
             "PCOISS_Post", "CASSS_C_Post", "CASSS_T_Post",
             "SRCS_Post_s1", "SRCS_Post_s2", "BESSP_Post_IRI")) {
  preds_dv <- setdiff(shared_preds, dv)
  result   <- impute_var(data, dv, preds_dv)
  data     <- result$data
}

# Combine imputed data with full dataset
data_combined <- d |>
  select(-any_of(names(data))) |>
  bind_cols(data) |>
  rename(
    Imputed_CASSSC_Pre  = Imputed_CASSS_C_Pre,
    Imputed_CASSSC_Post = Imputed_CASSS_C_Post,
    Imputed_CASSST_Pre  = Imputed_CASSS_T_Pre,
    Imputed_CASSST_Post = Imputed_CASSS_T_Post,
    Imputed_SRCSs1_Post = Imputed_SRCS_Post_s1,
    Imputed_SRCSs1_Pre  = Imputed_SRCS_Pre_s1,
    Imputed_SRCSs2_Pre  = Imputed_SRCS_Pre_s2,
    Imputed_SRCSs2_Post = Imputed_SRCS_Post_s2
  )
```

---

## 5. ANCOVA Models -- Post ~ Pre + Condition

### 5.1 Model specifications

```{r model-specs}
dv_list <- list(
  list(dv = "Imputed_BESST_Post_IRI", pre = "Imputed_BESST_Pre_IRI"),
  list(dv = "Imputed_BFSs_Post_INT",  pre = "Imputed_BFSs_Pre_INT"),
  list(dv = "Imputed_YSR_Post_INT",   pre = "Imputed_YSR_Pre_INT"),
  list(dv = "Imputed_PCOISS_Post",    pre = "Imputed_PCOISS_Pre"),
  list(dv = "Imputed_CASSSC_Post",    pre = "Imputed_CASSSC_Pre"),
  list(dv = "Imputed_CASSST_Post",    pre = "Imputed_CASSST_Pre"),
  list(dv = "Imputed_SRCSs1_Post",    pre = "Imputed_SRCSs1_Pre"),
  list(dv = "Imputed_SRCSs2_Post",    pre = "Imputed_SRCSs2_Pre"),
  list(dv = "Imputed_BESSP_Post_IRI", pre = "Imputed_BESSP_Pre_IRI")
)
```

### 5.2 Fit models and compute Cohen's d

Cohen's d for each coefficient is computed as `b_j / sigma(model)`, where sigma
is the model residual SD. For the Condition coefficients this gives an adjusted
mean-difference effect size in outcome SD units.

```{r fit-models, warning=FALSE}
# Validate and prep data for one model
prep_model_data <- function(dv, pre, data) {
  required <- c(dv, pre, "Condition")
  missing_cols <- setdiff(required, names(data))
  if (length(missing_cols) > 0)
    stop(paste("Missing columns:", paste(missing_cols, collapse = ", ")))
  df <- data |>
    select(all_of(required)) |>
    filter(if_all(everything(), ~ !is.na(.))) |>
    mutate(Condition = as.factor(Condition))
  if (nrow(df) < 10)
    stop(paste("Too few rows after NA removal for", dv))
  df
}

# Run one ANCOVA and return tidy results + Cohen's d
run_ancova <- function(dv, pre, data) {
  df      <- prep_model_data(dv, pre, data)
  formula <- as.formula(paste(dv, "~", pre, "+ Condition"))
  model   <- lm(formula, data = df)
  sigma   <- sigma(model)
  n       <- nrow(df)

  tidy(model, conf.int = TRUE) |>
    mutate(
      DV           = dv,
      Pre          = pre,
      Sample_Size  = n,
      Residual_SD  = sigma,
      Cohens_d     = estimate / sigma,
      Cohens_d_low = conf.low / sigma,
      Cohens_d_high= conf.high / sigma
    )
}

# Fit all models
all_results <- lapply(dv_list, function(spec) {
  tryCatch(
    run_ancova(spec$dv, spec$pre, data_combined),
    error = function(e) {
      warning(paste("Model failed for", spec$dv, ":", e$message))
      NULL
    }
  )
})

coef_table <- bind_rows(Filter(Negate(is.null), all_results))

# Print summary
cat("\nCoefficient table with Cohen's d for all models:\n")
print(coef_table |> select(DV, term, estimate, p.value, Cohens_d, Sample_Size))
```

### 5.3 Export effect size table

```{r export-effects}
write.csv(coef_table, "outputs/cohens_d_all_coefficients.csv", row.names = FALSE)
cat("Saved: outputs/cohens_d_all_coefficients.csv\n")
```

---

## 6. Regression Results Table (Formatted)

```{r regression-table, warning=FALSE}
regression_results <- lapply(dv_list, function(spec) {
  df  <- tryCatch(prep_model_data(spec$dv, spec$pre, data_combined), error = \(e) NULL)
  if (is.null(df)) return(NULL)
  mod <- lm(as.formula(paste(spec$dv, "~", spec$pre, "+ Condition")), data = df)
  tidy(mod, conf.int = TRUE) |>
    mutate(Model = spec$dv, N = nrow(df),
           sig = case_when(p.value < .001 ~ "***",
                           p.value < .01  ~ "**",
                           p.value < .05  ~ "*",
                           p.value < .10  ~ ".",
                           TRUE           ~ ""))
})

reg_df <- bind_rows(Filter(Negate(is.null), regression_results)) |>
  mutate(across(where(is.numeric), ~ round(., 3)))

reg_df |>
  kable(caption = "ANCOVA Regression Results -- Post ~ Pre + Condition") |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                full_width = FALSE)
```

---

## 7. Visualizations

### 7.1 Mean scores by time (pre/post) and condition

```{r mean-scores-plot, fig.width=14, fig.height=8}
mean_scores <- data_combined |>
  pivot_longer(cols = starts_with("Imputed_"),
               names_to = "Score_Type", values_to = "Score") |>
  separate(Score_Type, into = c("Prefix", "Measure", "Time"),
           sep = "_", extra = "merge") |>
  filter(Time %in% c("Pre", "Post")) |>
  group_by(Condition, Measure, Time) |>
  summarise(
    Mean_Score = mean(Score, na.rm = TRUE),
    SD_Score   = sd(Score, na.rm = TRUE),
    N          = sum(!is.na(Score)),
    SE         = SD_Score / sqrt(N),
    .groups = "drop"
  ) |>
  mutate(
    Time      = factor(Time, levels = c("Pre", "Post")),
    Condition = factor(Condition, levels = c("CBI, CICO", "CBI, RF", "CBI, CICO, RF"))
  )

# Filter to primary outcomes for cleaner plot
primary_measures <- c("BFSs", "YSR", "BESST", "PCOISS", "CASSSC", "CASSST")

plot_primary <- mean_scores |>
  filter(Measure %in% primary_measures) |>
  ggplot(aes(x = Time, y = Mean_Score,
             color = Condition, group = Condition)) +
  geom_line(linewidth = 0.8) +
  geom_point(size = 2) +
  geom_errorbar(aes(ymin = Mean_Score - SE, ymax = Mean_Score + SE),
                width = 0.1, alpha = 0.6) +
  facet_wrap(~ Measure, scales = "free_y") +
  scale_color_brewer(palette = "Set1") +
  labs(title = "Mean Scores by Condition and Time (Pre/Post)",
       x = "Time Point", y = "Mean Score", color = "Condition") +
  theme_minimal(base_size = 12) +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 45, hjust = 1))

ggsave("figures/mean_scores_by_time_with_error_bars.png",
       plot = plot_primary, width = 14, height = 8, dpi = 150)
print(plot_primary)
```

### 7.2 Descriptive statistics by condition (post-imputation)

```{r desc-post-imputation}
d_design_imp <- svydesign(id = ~1, data = data_combined, weights = NULL)

post_vars <- c("Imputed_BESST_Post_IRI", "Imputed_BFSs_Post_INT",
               "Imputed_YSR_Post_INT",   "Imputed_PCOISS_Post",
               "Imputed_CASSSC_Post",    "Imputed_CASSST_Post",
               "Imputed_SRCSs1_Post",    "Imputed_SRCSs2_Post")

post_by_cond <- bind_rows(lapply(
  intersect(post_vars, names(data_combined)),
  calc_cont_by_cond, design = d_design_imp
))

doc3 <- read_docx() |>
  body_add_par("Descriptive Statistics by Condition -- Post-Imputation",
               style = "heading 1") |>
  body_add_par("Posttest Outcomes by Condition", style = "heading 2") |>
  body_add_table(post_by_cond)
print(doc3, target = "outputs/Descriptive_Statistics_Report_Condition_Post.docx")
cat("Saved: outputs/Descriptive_Statistics_Report_Condition_Post.docx\n")
```

---

## 8. Session Info

```{r session-info}
sessionInfo()
```
